\LARGE \bf Multi-Armed Bandit Models for 2D Grasp Planning with Uncertainty

### 2015-06-15 paper.tex
.

\begin{algorithm}
 \KwResult{Current Best Arm, $\Gamma^*$ }
 For Beta($\alpha_{k,0}=1$,$\beta_{k,0}=1$) $\forall k \in K$ prior: \\
\For{ t=1,2,...}{ 
 Draw $p_{k,t} \sim$ Beta($\alpha_{k,t}$,$\beta_{k,t}$) for $k = 1,...,K$\\
 Pull $k_t  = \underset{k\in K}{\mbox{argmax}} \: p_{k,t}$\\
 Observe reward $R_{k,t} \in \lbrace 0,1 \rbrace$\\
 Update posterior:\\

 \eIf{$k = k_t$}{
 Set $\alpha_{k,t+1} = \alpha_{k,t} + R_{k_t,t}$ \\
 Set $\beta_{k,t+1} = \beta_{k,t} +1-R_{k_t,t}$\\
 }{
 Set $\alpha_{k,t+1} = \alpha_{k,t}$ \\
 Set $\beta_{k,t+1} = \beta_{k,t}$\\
 }
  }
 \caption{Thompson sampling for Beta-Bernoulli Process}
\end{algorithm}

@@

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
GPIS models of 2 example objects are visualized using the GPIS-Blur method of~\cite{mahler2015gp} in Figure \ref{fig:shape_samples}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
The measurement noise were assigned uniformly at random to the SDF.
We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
We  performed experiments for the case of two hard contacts in 2-D.
We drew random grasps $\Gamma$ by uniformly sampling the angle of the grasp axis around a circle with radius $\sqrt{2}
M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB 1600 MHz memory in Matlab 2013b.

>>>>

\begin{algorithm}
 \KwResult{Current Best Arm, $\Gamma^*$ }
 Initialize Beta($\alpha_{k,0}=1$,$\beta_{k,0}=1$) $\forall k \in K$ \\
\For{ t=1,2,...,N }{ 
 Draw $p_{k,t} \sim$ Beta($\alpha_{k,t}$,$\beta_{k,t}$) for $k = 1,...,K$\\
 Pull arm $k_t  = \underset{k\in K}{\mbox{argmax}} \: p_{k,t}$\\
 Observe reward $R_{k,t} \in \lbrace 0,1 \rbrace$\\
 %Update posterior:\\

 \eIf{$k = k_t$}{
 $\alpha_{k,t+1} \gets \alpha_{k,t} + R_{k_t,t}$ \\
$\beta_{k,t+1} \gets \beta_{k,t} +1-R_{k_t,t}$\\
 }{
$\alpha_{k,t+1} \gets \alpha_{k,t}$ \\
$\beta_{k,t+1} \gets \beta_{k,t}$\\
 }
  }
 \caption{Thompson sampling for Beta-Bernoulli Process}
\end{algorithm}

@@

\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown}, a database of 2D planar objects, as in \cite{christopoulos2007handling}.
We downsampled the silhouette by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was
observed and 0 if it was not observed, and a measurement noise map, which holds the variance of 0-mean noise added to the SDF values.
The measurement noise were assigned uniformly at random to the SDF.
We then construct a GPIS using the same method as proposed in~\cite{mahler2015gp}.
For illustrative purposes, the noise in approach, pose, and friction coefficient were set to the following variances $\sigma_{\psi}^2 = 0.2$ rads$^2$, $\sigma_{\by}^2 = 3$ grid cells$^2$, $\sigma_{\mu}^2 = 0.4$, $\sigma_{\phi}^2 = 0.3$ rads$^2$ and $\sigma_{\bt}^2 = 3$ grid cells$^2$.
We  performed experiments for the case of two hard contacts in 2-D.
We drew random grasps $\Gamma$ by uniformly sampling the angle of the grasp axis around a circle with radius $\sqrt{2}
M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin from a zero mean Gaussian with
variance 10 units$^2$. All experiments were run on a machine with OS X with a 2.7 GHz Intel core i7 processor and 16 GB
1600 MHz memory in Matlab 2013b. For illustration purposes, Figure \ref{fig:shape_samples} also displays
GPIS models of 2 real-world objects are visualized using the GPIS-Blur method~\cite{mahler2015gp}.
